\documentclass[12pt]{wrceletter}


\name{Dennis Evangelista}
\position{Assistant Professor}
%\email{\href{mailto:evangeli@usna.edu}{\emph{evangeli@usna.edu}}}
\email{evangeli@usna.edu}
\telephone{410-293-6132}

\date{\today}

\usepackage{designature}
\signature{\vspace*{-0.7in}\includesignature\\Dennis Evangelista}
%\signature{Dennis Evangelista\\Assistant Professor} % title not needed if in letterhead
\address{\null} %{105 Maryland Avenue\\Annapolis, MD 21402} % leave blank, provided in letterhead
%\longindentation=0in % to change signature to be flushleft

\begin{document}
\begin{letter}{% recipient address here
Selection Committee}

% opening here
\opening{}
\raggedright 
\setlength{\parindent}{15pt}

This letter is in support of MIDN 1/c Bryan Phan's application to the Schwarzman Scholarship. Mr.~Phan is a student in my department, the Department of Weapons, Robotics, and Control Engineering at the United States Naval Academy. This term, I am working closely with him on a senior capstone engineering design project to develop unmanned aerial systems (UAS) for science survey and sample return missions aimed at protecting known endangered, endemic, and difficult to sample species on islands (as well as potentially finding new species). 
 
Our department focuses on robotics and control, autonomy, and automatic control applied to a wide variety of applications. Our students study subjects drawn from mechanical and electrical engineering, programming, use of embedded microcontrollers, linear and modern controls, and engineering design, while also completing training in leadership in preparation to become junior officers in the Navy or Marine Corps. In addition, Mr.~Phan has prior service in the United States Marine Corps as an enlisted tactical air traffic controller. This is relatively rare among our students, and is a mark of special excellence and trust in his ability to lead and inspire his future platoon or divison. For my project, I am quite excited to have a gentleman motivated to study autonomy and control as applied to UAS who also has field experience controlling aerial assets from the ground. 
 
Mr.~Phan is minoring in Mandarin at USNA and completed study abroad in Beijing; he is also a native speaker of TeoChew, is active in Asian cultural communities here at USNA, and has served in the Brigade in leadership and counseling billets. For my project, these also assure me he will be an asset when doing science in the field with people of diverse backgrounds. 

Mr.~Phan is a respectful person of honor, character, and itegrity who is intensly dedicated to success as a leader. In my observations of him with his capstone team, he is self-aware and self-reflective, is a courageous risk taker, is well-liked by his peers, and appears well suited to fit into many social settings. Taken together, I believe Mr.~Phan has great potential to succeed in the Schwartzman program. 

\closing{~} % provides empty 

%\ps{post script here}
%\encl{enclosure here}
\end{letter}
\end{document}

%Some bullet points of what I would like you to say are:  
%Respectful person of Honor, Character and Integrity
%Intensely dedicated to success in my leadership  
%Self-Aware and Self-Reflective 
%High Emotion Intelligence
%Relentlessly Ambitious
%Courageous Risk-taker
%Well-liked and can fit into any social setting
